GPU-friendly Stroke Expansion

### 2024-06-13 paper.tex
Address feedback on section 8 edits

A property of the data-parallel structure is that the output of the compute stage is unordered. The cubic-Bézier-to-Euler-spiral conversion is sequential within a single thread, so it is possible to preserve ordering at the scope of an individual path segment, if desired. However, ordering cannot be guaranteed across path segments. We refer to this output data structure as \emph{line soup}. An application may want to sort the line soup, depending on the requirements of the chosen rendering algorithm. For instance, our own renderer employs tile-based scanline rasterization in a compute shader, with a pipeline architecture that resembles \emph{cudaraster} (\citet{Laine2011}) and \emph{MPVG} (\citet{Ganacim2014}). In this design, the line soup elements are spatially sorted by subsequent compute stages into a grid of 16x16 pixel tiles. The final compute stage of our renderer (called \emph{fine rasterizer}) operates at tile granularity and computes pixel coverage for filled polygons outlined by the line soup (the details of which are beyond the scope of this paper).

@@

The compute shader writes the line soup output to a GPU storage buffer. Each line soup entry contains the viewport coordinates of the two endpoints of a singe line segment. We also implemented a variant that outputs circular arc segments instead of lines, in which the output entries contain the arc endpoints in addition to its curvature. For both primitive types, our renderer also outputs a 32-bit \emph{path ID} used by downstream pipeline stages to identify the path that a segment belongs to, in order to retrieve the correct paint (solid or gradient color) for rendering.

>>>>

The output of the compute shader is a collection of line segments that gets stored in a GPU storage buffer. Every element in the output contains the viewport coordinates of the two endpoints of a single line segment. A property of the data-parallel structure is that the line segments are unordered. Because the segments are processed in parallel, ordering cannot be guaranteed across path segments. We refer to this output data structure as \emph{line soup}.

An application may want to sort the line soup, depending on the requirements of the chosen rendering algorithm. For instance, our own renderer employs tile-based scanline rasterization in a compute shader, with a pipeline architecture that resembles \emph{cudaraster}[\citenum{Laine2011}] and \emph{MPVG}[\citenum{Ganacim2014}]. In this design, the line soup elements are spatially sorted by subsequent compute stages into a grid of 16x16 pixel tiles. The final compute stage of our renderer (called \emph{fine rasterizer}) operates at tile granularity and computes pixel coverage for filled polygons outlined by the line soup (Figure~\ref{fig:pipeline} illustrates the overall structure of our renderer, the details of which are beyond the scope of this paper).

@@

We also implemented a variant that outputs circular arc segments instead of lines, in which the output entries contain the arc endpoints in addition to its curvature. For both primitive types, our renderer also outputs a 32-bit \emph{path ID} used by downstream pipeline stages to identify the path that a segment belongs to, in order to retrieve the correct paint (solid or gradient color) for rendering.
